Transition to online labs at ECU

### 2020-11-17 readingDaySeminar/PICUP-ECULabs.tex
Updated a few files.  Getting the reading day seminar ready.

\documentclass[aspectratio=169]{beamer}
% \usepackage{beamerthemesplit} % Activate for custom appearance
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[export]{adjustbox}
\usetheme{Boadilla}
\usecolortheme{seahorse}
\usefonttheme[stillsansseriflarge]{serif}
\title[ECU online labs]{Transition to online labs at ECU}
\author[Sprague and Wolf]{Mark W.\ Sprague and Steven F.\ Wolf}
\institute[ECU]{East Carolina University}
\date{\today}
\definecolor{ECUPurple}{RGB}{80,45,127}

@@

\begin{frame}
\frametitle{Tools used in online lab delivery}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{cll}
\hline\hline
\textbf{Tool} & \textbf{Use} & \textbf{Rationale} \\
\hline
Canvas & \parbox[t]{2in}{\raggedright Material, Assignments, Quizzes, Discussions }& University LMS\\
WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
Peergrade.io & \parbox[t]{2in}{\raggedright Online peer review} & \parbox[t]{2in}{\raggedright Anonymous reviews and feedback; better than Canvas}\\
Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} & Fine-grained control\\[3ex]
\hline\hline
\end{tabular}
\end{center}
\end{frame}

>>>>

\documentclass[aspectratio=169,shadow=true]{beamer}
% \usepackage{beamerthemesplit} % Activate for custom appearance
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[export]{adjustbox}
\usetheme{Boadilla}
\usepackage{ecuPresentation}

\title[ECU online labs]{Transition to online labs at ECU}
\author[Sprague and Wolf]{Mark W.\ Sprague and Steven F.\ Wolf}
\institute[ECU]{East Carolina University}
\date{\today}
\definecolor{ECUPurple}{RGB}{80,45,127}

@@

{\nologo
\begin{frame}
\frametitle{Tools used in online lab delivery}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{cll}
\hline\hline
\textbf{Tool} & \textbf{Use} & \textbf{Rationale} \\
\hline
Canvas & \parbox[t]{2in}{\raggedright Material, Assignments, Quizzes, Discussions }& University LMS\\
WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
Canvas & \parbox[t]{2in}{\raggedright Online peer review} & \parbox[t]{2in}{\raggedright Anonymous reviews and feedback}\\
Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} & Fine-grained control\\[3ex]
\hline\hline
\end{tabular}
\end{center}
\end{frame}
}
